Distrivia: A Distributed Trivia Game

### 2011-04-22 papers/phase-two/paper.tex
Fix double the
Updated Whats Left for web client

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
While private games are implemented on the server, 
Also, when a user clicks on a button to do something like log in, the button should be disabled while waiting for a response,
alternatively it needs to be able to handle sending out two calls for the same request and not getting confused if it gets two back.
\subsection {Android}
Private gameplay is the largest thing left for the android client. Besides this we've just been fixing bugs and cleaning up the UI.
\subsection {iPhone}
The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
and competing in rounds.

>>>>

\section {What's Left}
\subsection {Server}
The server is nearly completed. The server application just needs to have some tweaks and further testing.
\subsection {Web Client}
A lot of the main features of the web client are completed.
However, there are still a few remaining features that need to be implemented.
The only major feature remaining is private games, which are largely unstarted, although it will reuse most of the public game code.
In addition to this, buttons should be disabled when clicked to prevent users from spamming the server with repeat messages.
\subsection {Android}
Private gameplay is the largest thing left for the android client. Besides this we've just been fixing bugs and cleaning up the UI.
\subsection {iPhone}
The iPhone application just started development in the last couple days. We have built most of the UI but need to connect all of the actions
to the server. We will need to implement everything, including login/registration, joining public/private games, viewing leaderboards,
and competing in rounds.
